Bayesian Neural Arithmetic Units -- Leveraging The Complex Plane

### 2020-04-22 paper/main.tex
start writing

@@

It is known that Neural Networks can approximate functions arbitrarily well but
do not necessarily generalize beyond the range inputs that were seen during
training. Neural Arithmetic Units can help to overcome this problem
\cite{trask_neural_2018,madsen_neural_2020}

% TODO: put this in acknowledgements %
all the results in this paper were create with the help of the following Julia
packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)

>>>>

\usepackage{todonotes}

@@

It is known that Neural Networks can approximate functions arbitrarily
well\todo{cite universal approx}.  However, this strength of approximation
often comes at the cost of generalization beyond the training data manifold.
\citet{trask_neural_2018} have demonstrated how severe this problem is even for
the simplest arithmetic operations, such as summing or multiplying two numbers.
In order to increase the power of abstraction of Neural Networks they propose a
\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this problem
\cite{trask_neural_2018} and is capable of learning the arithmetic addition
$+$, subtraction $-$, multiplication $\times$, and division
$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.
However, the NALU comes with the severe limitation not being able to handle negative
inputs due to the logarithm in the multiplication part of the NALU:
\begin{align}
  \label{eq:nalu}
  \text{Addition: }       & \bm a = \bm W \bm x                  
                          & \bm W& = \tanh(\hat{\bm W}) \odot \sigma(\hat{\bm M}) \\
  \text{Multiplication: } & \bm m = \exp \bm W(\log(|\bm x|+\epsilon)) & &\\
  \text{Output: }         & \bm y = \bm a \odot \bm g + \bm m \odot (1-\bm g) 
                          & \bm g& = \sigma(\bm G\bm x)
\end{align}

A multiplication layer that can handle negative inputs was introduced by \citet{madsen_neural_2020}.
The \emph{Neural Multiplication Unit} (NMU) is defined by
\begin{align}
  \text{NMU: } y_j = \prod_i W_{ij} z_{i} + 1 - W_{ij} \hskip .2\textwidth W_{ij}=\min(\max(W_{ij}, 0), 1)
\end{align}

\todo{put this in acknowledgements
all the results in this paper were create with the help of the following Julia
packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
